### 2021-05-19 content/31.tooling-table.tex
Changes from Nick and others
Reviews, credits, formal definitions in tex
Updates from Overleaf

\begin{table}[htbp]
	\centering
	\begin{tabular}{llll}
		\toprule
		\textbf{Tool name} & Targets & Language / Platform & Status \\
		\multicolumn{4}{l}{\it Brief Description} \\
		\midrule

@@

		\textbf{Life Monitor} \citep{about-lifemonitor} & Workflow developers & Python & Beta \\
		\multicolumn{4}{l}{\it Workflow testing and monitoring service; Workflow Testing profile of RO-Crate} \\

@@

>>>>

% Please update in 31.tooling-table.md first!
\begin{table}[htbp]
	\centering
	\begin{tabular}{llll}
		\toprule
		\textbf{Tool name} & Targets & Language / Platform & Status \\
		\multicolumn{4}{l}{\it Brief Description} \\
		\midrule

@@

		\textbf{Life Monitor} \citep{about-lifemonitor} & Workflow developers & Python & Alpha \\
		\multicolumn{4}{l}{\it Workflow testing and monitoring service; Workflow Testing profile of RO-Crate} \\

@@

        \textbf{CheckMyCrate} \citep{CheckMyCrate} & Developers & Python (CLI) & Alpha \\
        \multicolumn{4}{l}{\it Validation according to Workflow RO-Crate profile} \\
